Discovering governing reactions from concentration data

### 2018-01-25 docs/manuscript.tex
different wording

	When presented with multiple trajectories one can extend the objective function by a sum over these and obtain a more general minimization problem that reads: Find $\hat{\Xi}$ such that
	\begin{align}
		\hat{\Xi} = \underset{\Xi}{\arg\min}\left( \sum_{\text{traj}}\frac{1}{2T_{\text{traj}}}\left\| \dot{\textbf{X}_\text{traj}} - \Theta(\textbf{X}_\text{traj})\Xi \right\|_F^2 + \alpha\lambda\|\Xi\|_1 + \alpha(1-\lambda)\|\Xi\|_2^2 \right)
	\end{align}
	subject to $\Xi\geq 0$. (\textcolor{red}{this probably should be motivated better})

	For $\alpha=0$ the minimization problem reduces to constrained least-squares. In order to solve (\ref{method:minimizationproblem}) we apply the sequential least-squares minimizer SLSQP, originally described in \cite{Kraft1988}, by the software package SciPy \cite{SciPy}. As initial guess for the regularized problem we use the solution of (\ref{method:minimizationproblem}) with $\alpha=0$.

@@

>>>>

	When presented with multiple trajectories one can extend the objective function by a sum over these and obtain a more general minimization problem that reads: Find $\hat{\Xi}$ such that
	\begin{align}
		\hat{\Xi} = \underset{\Xi}{\arg\min}\left( \sum_{\text{traj}}\frac{1}{2T_{\text{traj}}}\left\| \dot{\textbf{X}}_\text{traj} - \Theta(\textbf{X}_\text{traj})\Xi \right\|_F^2 + \alpha\lambda\|\Xi\|_1 + \alpha(1-\lambda)\|\Xi\|_2^2 \right)
	\end{align}
	subject to $\Xi\geq 0$.
	For $\alpha=0$ the minimization problem reduces to constrained least-squares. In order to solve (\ref{method:minimizationproblem}) we apply the sequential least-squares minimizer SLSQP, originally described in \cite{Kraft1988}, by the software package SciPy \cite{SciPy}. As initial guess for the regularized problem we use the solution of (\ref{method:minimizationproblem}) with $\alpha=0$.

@@

    \section{Scenarios of measurement}

    The proposed estimation method is designed to find reaction networks and rates from experimental data. Therefore one can define the following measurement scenarios, that differentiate how many timeseries are available and how much noise is contained in the data:
    \begin{enumerate}
        \item The initial state of the measurement apparatus can be reproduced exactly. There is only one set of generating reaction rates. Each datapoint is subject to noise. The outcome of this scenarios is one time-series of concentrations with a certain noise-level.
        \item The process is observed multiple times. The initial state of the measurement apparatus differs in each observation. The outcome of this scenario is multiple time-series each with a given noise level and different initial states.
        \item The process is observed multiple times. The initial state of the measurement apparatus differs in each observation. Additionally the generating reaction rates slightly differ in each observation. The outcome of this scenario is multiple time-series each with a given noise level, different initial states and slighty perturbed underlying reaction rates.
    \end{enumerate}
